ODGI: understanding pangenome graphs

### 2021-10-14 manuscript/main.tex
going for node struct model
make the node struct

\usepackage[draft]{hyperref}
\usepackage{makecell}
\usepackage{comment}
\usepackage{subcaption}

@@

We store the graph in a vector of node structures, each of which presents a node-local view of the graph sequence, topology, and path layout.
Expressed in terms of the variation graph $V$, the structure for node  the node sequence $seq(n_i)$

>>>>

\usepackage[draft]{hyperref}
\usepackage{makecell}
\usepackage{comment}
\usepackage{subcaption}
\usepackage{algorithm2e}

\SetAlgoLined
\SetKwProg{MyStruct}{Struct}{ contains}{end}

@@

We store the graph in a vector of node structures, each of which presents a node-local view of the graph sequence, topology, and path layout.
Expressed in terms of the variation graph $V$, ODGI's core $Node$ structure includes.

\begin{algorithm}
\MyStruct{Node}{
    \textbf{id} $\in \mathbb{N}$ \tcp{an identifier}
    \textbf{lock} \tcp{atomic locking primitive}
    \textbf{sequence} $= [ATGC]*$ \tcp{DNA, RNA, protein}
    \tcp{succinct dynamic bitvector of edges}
    \textbf{edges} $= (s_{x},s_{y})* : x \land y \in$ decoding \\
    \tcp{a vector of id deltas}
    \textbf{decoding} $= (1 \ldots x \ldots N)*$ \\
    \tcp{a vector of path steps}
    \textbf{paths}
}
\caption{ODGI's relativistically-packed node structure.}
\end{algorithm}

\begin{comment}
TODO:
    struct step_t {
        uint64_t path_id;
        bool is_rev;
        bool is_start;
        bool is_end;
        uint64_t prev_id;
        uint64_t prev_rank;
        uint64_t next_id;
        uint64_t next_rank;
    };
\end{comment}

%\begin{enumerate}
%\item a node sequence $seq(n_i)$
%\end{enumerate}
